---
title: "Capital in Twenty First Century by Thomas Piketty."
output: 
  flexdashboard::flex_dashboard:
    #storyboard: true
    social: menu
    #source: embed
---


```{r setup, include=FALSE}

#Clear the workspace - remove all variables
rm(list = ls())

library(Quandl)
library(plotly)

library(flexdashboard)

```


```{r}
titleVar  <- list(
          #family = "Ariel",
          size = 18
          #color = "#7f7f7f"
          )
```

Introduction {.storyboard}
=========================================

### <b>Income inequality in the United States, 1910-2010</b>

```{r}

i1 <- Quandl("PIKETTY/TSI_1", api_key="yg2rjFAWcN1FgzoJ1naL")

plot_ly(i1, x=i1$Date, y=i1$Value, mode = 'lines+markers', type = "scatter") %>%
  layout(title = '<b>Income inequality in the United States, 1910-2010</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Share of top decile in national income</b>'))


```

***

Introduction

- FIGURE I.1

- page 36

- Context 



### <b>The capital/income ratio in Europe, 1870-2010</b>

```{r}


i2 <- Quandl("PIKETTY/TSI_2", api_key="yg2rjFAWcN1FgzoJ1naL")


plot_ly(i2, x=i2$Date, y = i2$Germany, name = "<b>Germany</b>", mode = 'lines+markers', type='scatter') %>%
  add_trace(x=i2$Date, y = i2$France,  name = "<b>France</b>", connectgaps = TRUE) %>%
  add_trace(x=i2$Date, y = i2$Britain, name = "<b>Britain</b>", connectgaps = TRUE) %>%
  layout(title = '<b>The capital/income ratio in Europe, 1870-2010</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Market value of private capital (% national income)</b>'))


```

***

Introduction

- FIGURE I.2

- Page 38

- Context


Part One {.storyboard}
=========================================

### <b>The distribution of world output, 1700-2012</b>

```{r}

c1_1 <- Quandl("PIKETTY/TS1_1A", api_key="yg2rjFAWcN1FgzoJ1naL")

#GP: taking first 8 rows only, data since 1700 AD
c1_1 <- c1_1[1:8,]

#NOTE: code below gave none stacked graph, we need to stack one on top of another 
# plot_ly(data=c1_1, x=Date, y=`World output`, fill="tonexty", mode="lines")  %>%
#            add_trace(x=Date, y = Europe, fill="tonexty") %>%
#            add_trace(x=Date, y = America, fill="tonexty") %>%
#            add_trace(x=Date, y = Africa, fill="tonexty") %>%
#            add_trace(x=Date, y = Asia, fill="tonexty")
               


Years <- c1_1$Date
y1_real<- c1_1$Europe
y2_real<- c1_1$America
y3_real<- c1_1$Africa
y4_real<- c1_1$Asia




df= data.frame(Years, y1_real, y2_real, y3_real, y4_real)

df$y4_stck<- df$y4_real + df$y3_real + df$y2_real + df$y1_real
df$y3_stck<- df$y3_real + df$y2_real + df$y1_real
df$y2_stck<- df$y2_real + df$y1_real
df$y1_stck<- df$y1_real
 

 p1<- plot_ly(df, x=df$Years, y=df$y1_stck, text=df$y1_real, hoverinfo='x+text+name', name="Europe", fill="tonexty", type = 'scatter', mode = "markers") %>%
   layout(title = '<b>The distribution of world output, 1700-2012</b>',
          titlefont = titleVar,
          xaxis = list(title = '<b>Years</b>'),
          yaxis = list (title = '<b>Percentage of Total World Output</b>'))
 
 
 p2<- add_trace(p1, x=df$Years, y=df$y2_stck, text=df$y2_real, type = 'scatter', mode = "markers", hoverinfo='x+text+name', name="America", fill="tonexty")
 p3<- add_trace(p2, x=df$Years, y=df$y3_stck, text=df$y3_real, type = 'scatter', mode = "markers", hoverinfo='x+text+name', name="Africa", fill="tonexty") 
 p4<- add_trace(p3, x=df$Years, y=df$y4_stck, text=df$y4_real, type = 'scatter', mode = "markers", hoverinfo='x+text+name', name="Asia", fill="tonexty") 
      
p4

rm(df, p1, p2, p3, p4, y1_real, y2_real, y3_real, y4_real, Years)


```

***

Part One: Income and Capital

- Income and Output

- FIGURE 1.1

- Page 75

- Context 


### <b>The distribution of world population, 1700-2012</b>

```{r}



c1_2 <- Quandl("PIKETTY/TS1_2A", api_key="yg2rjFAWcN1FgzoJ1naL")


#GP: taking first 8 rows only, data since 1700 AD
c1_2 <- c1_2[1:8,]


Years <- c1_2$Date
y1_real<- c1_2$Europe
y2_real<- c1_2$America
y3_real<- c1_2$Africa
y4_real<- c1_2$Asia


df= data.frame(Years, y1_real, y2_real, y3_real, y4_real)

df$y4_stck<- df$y4_real + df$y3_real + df$y2_real + df$y1_real
df$y3_stck<- df$y3_real + df$y2_real + df$y1_real
df$y2_stck<- df$y2_real + df$y1_real
df$y1_stck<- df$y1_real

p1<- plot_ly(df, x=df$Years, y=df$y1_stck, text=df$y1_real, type = 'scatter', mode = "markers", hoverinfo='x+text+name', name="Europe", fill="tonexty") %>%
  layout(title = '<b>The distribution of world population, 1700-2012</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Percentage of Total World Population</b>'))


p2<- add_trace(p1, x=df$Years, y=df$y2_stck, type = 'scatter', mode = "markers", text=df$y2_real, hoverinfo='x+text+name', name="America", fill="tonexty")
p3<- add_trace(p2, x=df$Years, y=df$y3_stck, type = 'scatter', mode = "markers", text=df$y3_real, hoverinfo='x+text+name', name="Africa", fill="tonexty")
p4<- add_trace(p3, x=df$Years, y=df$y4_stck, type = 'scatter', mode = "markers", text=df$y4_real, hoverinfo='x+text+name', name="Asia", fill="tonexty")

p4

rm(df, p1, p2, p3, p4, y1_real, y2_real, y3_real, y4_real, Years)

```

***
Part One: Income and Capital

- Income and Output

- FIGURE 1.2

- Page 76

- Context 




### <b>Global inequality, 1700-2012: divergence then convergence ?</b>

```{r}


c1_3 <- Quandl("PIKETTY/TS1_3A", api_key="yg2rjFAWcN1FgzoJ1naL")

c1_3 <- c1_3[1:8,]


plot_ly(c1_3, x=c1_3$Date, y=c1_3$`Europe + America`, name = "<b>Europe + America</b>", mode = 'lines+markers', type = 'scatter') %>%
  add_trace(x=c1_3$Date, y = c1_3$`Asia + Africa`, name = "<b>Asia + Africa</b>", connectgaps = TRUE) %>%
  add_trace(x=c1_3$Date, y = c1_3$`Per capita output`, name = "<b>World</b>", connectgaps = TRUE) %>%
  layout(title = '<b>Global inequality, 1700-2012: divergence then convergence?</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Per capita GDP(% of World Average)</b>'))



```

***

Part One: Income and Capital

- Income and Output

- FIGURE 1.3

- Page 77

- Context 



### <b>Exchange rate and purchasing power parity: euro/dollar</b>

```{r}

c1_4 <- Quandl("PIKETTY/TS1_7", api_key="Kv-CaGGQMdMbP2q7nER2")


plot_ly(c1_4, x=c1_4$Date, y=c1_4$`exchange rate euro/dollar`, name = "<b>Exchange rate euro/dollar</b>", 
                                                               mode = 'lines+markers',
                                                               type = 'scatter',
                                                               marker = list(symbol = 'square')) %>%
  add_trace(x=c1_4$Date, y = c1_4$`purchasing power parity euro/dollar`, name = "<b>Purchasing power parity euro/dollar</b>", 
                                                                    mode = 'lines+markers',  
                                                                    type = 'scatter',
                                                                    marker = list(symbol = "triangle-up-open"),
                                                                    connectgaps = TRUE) %>%
  layout(title = '<b>Exchange rate and purchasing power parity: euro/dollar</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b></b>'))

```

***


Part One: Income and Capital

- Income and Output

- FIGURE 1.4

- Page 82

- Context 



### <b>Exchange rate and purchasing power parity: euro/yuan</b>

```{r}


#c1_4 <- Quandl("PIKETTY/TS1_7", api_key="Kv-CaGGQMdMbP2q7nER2")


plot_ly(c1_4, x=c1_4$Date, y= c1_4$`exchange rate euro/yuan`, name = "<b>Exchange rate euro/yuan</b>", 
                                                              mode = 'lines+markers',  
                                                              type = 'scatter',
                                                              marker = list(symbol = 'square')) %>%
  add_trace(x=c1_4$Date, y = c1_4$`purchasing power parity euro/yuan`, name = "<b>Purchasing power parity euro/yuan</b>", 
                                                                       mode = 'lines+markers',  
                                                                       type = 'scatter',
                                                                     marker = list(symbol = "triangle-up-open"),
                                                                connectgaps = TRUE) %>%
  layout(title = '<b>Exchange rate and purchasing power parity: euro/yuan</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b></b>'))


```

***


Part One: Income and Capital

- Income and Output

- FIGURE 1.5

- Page 85

- Context 




### <b>The growth of world population, 1700-2012</b>

```{r}

c2_1 <- Quandl("PIKETTY/TS2_2C", api_key="Kv-CaGGQMdMbP2q7nER2", start_date="1700-01-01")


c2_1 <- c2_1[5:11,]

Years <- c2_1$Year
y1_real<- c2_1$Europe
y2_real<- c2_1$Amrica
y3_real<- c2_1$Africa
y4_real<- c2_1$Asia


df= data.frame(Years, y1_real, y2_real, y3_real, y4_real)

df$y4_stck<- df$y4_real + df$y3_real + df$y2_real + df$y1_real
df$y3_stck<- df$y3_real + df$y2_real + df$y1_real
df$y2_stck<- df$y2_real + df$y1_real
df$y1_stck<- df$y1_real

p1<- plot_ly(df, x=df$Years, y=df$y1_stck, text=df$y1_real, hoverinfo='x+text+name', 
                                                            name="Europe", 
                                                            mode = 'lines+markers',  
                                                            type = 'scatter',
                                                            fill="tonexty") %>%
  layout(title = '<b>The growth of world population, 1700-2012</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>World population (million inhabitants)</b>'))


p2<- add_trace(p1, x=df$Years, y=df$y2_stck, text=df$y2_real, hoverinfo='x+text+name', name="America", fill="tonexty")
p3<- add_trace(p2, x=df$Years, y=df$y3_stck, text=df$y3_real, hoverinfo='x+text+name', name="Africa", fill="tonexty")
p4<- add_trace(p3, x=df$Years, y=df$y4_stck, text=df$y4_real, hoverinfo='x+text+name', name="Asia", fill="tonexty")

p4 


rm(df, p1, p2, p3, p4, y1_real, y2_real, y3_real, y4_real, Years)


```

***


Part One: Income and Capital

- Growth: Illusions and Realities

- FIGURE 2.1

- Page 95

- Context 




### <b>The growth rate of world population from Antiquity to 2100</b>

```{r}

c2_2 <- Quandl("PIKETTY/TS2_2A", api_key="Kv-CaGGQMdMbP2q7nER2")

plot_ly(c2_2, x=c2_2$`Year Ending`, y=c2_2$World, mode = 'lines+markers',  marker = list(symbol = 'square'), type='scatter') %>%
  layout(title = '<b>The growth rate of world population from Antiquity to 2100</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>World Population growth rate</b>'))

```

***


Part One: Income and Capital

- Growth: Illusions and Realities

- FIGURE 2.2

- Page 101

- Context 






### <b>The growth rate of per capita output since the Industrial Revolution</b>

```{r}

c2_3 <- Quandl("PIKETTY/S2_3", api_key="Kv-CaGGQMdMbP2q7nER2")
  
c2_3 <- c2_3[5:11,]

plot_ly(c2_3, x=c2_3$`Year Ending`, y=c2_3$`Western Europe`, name = "<b>Western Europe</b>", 
                                                             mode = 'lines+markers', 
                                                             type = 'scatter',
                                                             marker = list(symbol = 'square')) %>%
  add_trace(x=c2_3$`Year Ending`, y = c2_3$`North America`, name = "<b>North America</b>", 
                                                            mode = 'lines+markers', 
                                                            type = 'scatter',
                                                            marker = list(symbol = 'square'),
                                                            connectgaps = TRUE) %>%
  
  layout(title = '<b>The growth rate of per capita output since the Industrial Revolution</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Growth rate of per capita GDP</b>'))
  
```

***


Part One: Income and Capital

- Growth: Illusions and Realities

- FIGURE 2.3

- Page 122

- Context 






### <b>The growth rate of world per capita output from Antiquity to 2100</b>

```{r}

c2_4 <- read.csv("./c2_4.csv", header = TRUE)
  

plot_ly(c2_4, x=c2_4$Years, y=c2_4$Per.capita.world.output, mode = 'lines+markers', 
                                                            type = 'scatter',
                                                            marker = list(symbol = 'square')) %>%
  layout(title = '<b>The growth rate of world per capita output from Antiquity to 2100</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Growth rate of per capita GDP</b>'))
  
```

***


Part One: Income and Capital

- Growth: Illusions and Realities

- FIGURE 2.4

- Page 125

- Context 




### <b>The growth rate of world output from Antiquity to 2100</b>

```{r}

plot_ly(c2_4, x=c2_4$Years, y=c2_4$World.output, mode = 'lines+markers', 
                                                 type = 'scatter',
                                                 marker = list(symbol = 'square')) %>%
  layout(title = '<b>The growth rate of world output from Antiquity to 2100</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Growth rate World GDP</b>'))
  
```

***


Part One: Income and Capital

- Growth: Illusions and Realities

- FIGURE 2.5

- Page 127

- Context 






### <b>Inflation since the Industrial Revolution</b>

```{r}

c2_5 <- Quandl("PIKETTY/S2_5", api_key="Kv-CaGGQMdMbP2q7nER2")
  

plot_ly(c2_5, x=c2_5$`Year Ending`, y=c2_5$France,  name="<b>France</b>", mode = 'lines+markers', type = 'scatter') %>%
  add_trace(x=c2_5$`Year Ending`, y=c2_5$Germany, name="<b>Germany</b>", mode = 'lines+markers',
                                                 marker = list(symbol = 'triangle-up')) %>%
  add_trace(x=c2_5$`Year Ending`, y=c2_5$`United States`, name="<b>United States</b>", mode = 'lines+markers',
                                                 marker = list(symbol = 'triangle-up-open')) %>%
  add_trace(x=c2_5$`Year Ending`, y=c2_5$Britain, name="<b>Britian</b>", mode = 'lines+markers',
                                                 marker = list(symbol = 'square-open')) %>%
  layout(title = '<b>Inflation since the Industrial Revolution</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Inflation rate(consumer price index)</b>'))
  
```

***


Part One: Income and Capital

- Growth: Illusions and Realities

- FIGURE 2.6

- Page 135

- Context 




Part Two {.storyboard}
=========================================


### <b>Capital in Britain, 1700-2010</b>

```{r}

c3_1 <- Quandl("PIKETTY/T3_1", api_key="Kv-CaGGQMdMbP2q7nER2")

#GP: taking first 8 rows only, data since 1700 AD
c3_1 <- c3_1[,1:6]


Years <- c3_1$Year
y1_real<- c3_1$`incl. Land`
y2_real<- c3_1$`incl. Housing`
y3_real<- c3_1$`incl. Other domestic capital assets`
y4_real<- c3_1$`incl. Net foreign capital`



df= data.frame(Years, y1_real, y2_real, y3_real, y4_real)

df$y4_stck<- df$y4_real + df$y3_real + df$y2_real + df$y1_real
df$y3_stck<- df$y3_real + df$y2_real + df$y1_real
df$y2_stck<- df$y2_real + df$y1_real
df$y1_stck<- df$y1_real

p1<- plot_ly(df, x=df$Years, y=df$y1_stck, text=df$y1_real, mode = 'lines+markers', 
                                                            type = 'scatter', 
                                                            hoverinfo='x+text+name', 
                                                            name="Agricultural land", 
                                                            fill="tonexty") %>%
  layout(title = '<b>Capital in Britain, 1700-2010</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Value of national capital(% of national income)</b>'))


p2<- add_trace(p1, x=df$Years, y=df$y2_stck, text=df$y2_real, hoverinfo='x+text+name', name="Housing", fill="tonexty")
p3<- add_trace(p2, x=df$Years, y=df$y3_stck, text=df$y3_real, hoverinfo='x+text+name', name="Other domestic capital", fill="tonexty")
p4<- add_trace(p3, x=df$Years, y=df$y4_stck, text=df$y4_real, hoverinfo='x+text+name', name="Net foreign capital", fill="tonexty")

p4
 
# p5<- layout(yaxis=list(showgrid=FALSE, showline=FALSE))
# p5

rm(df, p1, p2, p3, p4, p5, y1_real, y2_real, y3_real, y4_real, Years)



```

***


Part Two: THE DYNAMICS OF THE CAPITAL/INCOME RATIO

- The Metamorphoses of Capital

- FIGURE 3.1

- Page 142

- Context 




### <b>Capital in France, 1700-2010</b>

```{r}

c3_2 <- Quandl("PIKETTY/T3_2", api_key="Kv-CaGGQMdMbP2q7nER2")

#GP: taking first 8 rows only, data since 1700 AD
c3_2 <- c3_2[,1:6]


Years <- c3_2$Year
y1_real<- c3_2$`incl. Land`
y2_real<- c3_2$`incl. Housing`
y3_real<- c3_2$`incl. Other domestic capital assets`
y4_real<- c3_2$`incl. Net foreign capital`



df= data.frame(Years, y1_real, y2_real, y3_real, y4_real)

df$y4_stck<- df$y4_real + df$y3_real + df$y2_real + df$y1_real
df$y3_stck<- df$y3_real + df$y2_real + df$y1_real
df$y2_stck<- df$y2_real + df$y1_real
df$y1_stck<- df$y1_real

p1<- plot_ly(df, x=df$Years, y=df$y1_stck, text=df$y1_real, mode = 'lines+markers', 
                                                            type = 'scatter', 
                                                            hoverinfo='x+text+name', 
                                                            name="Agricultural land", 
                                                            fill="tonexty") %>%
  layout(title = '<b>Capital in France, 1700-2010</b>',
         titlefont = titleVar,
         xaxis = list(title = '<b>Years</b>'),
         yaxis = list (title = '<b>Value of national capital(% of national income)</b>'))


p2<- add_trace(p1, x=df$Years, y=df$y2_stck, text=df$y2_real, hoverinfo='x+text+name', name="Housing", fill="tonexty")
p3<- add_trace(p2, x=df$Years, y=df$y3_stck, text=df$y3_real, hoverinfo='x+text+name', name="Other domestic capital", fill="tonexty")
p4<- add_trace(p3, x=df$Years, y=df$y4_stck, text=df$y4_real, hoverinfo='x+text+name', name="Net foreign capital", fill="tonexty")

p4

# p5<- layout(yaxis=list(showgrid=FALSE, showline=FALSE))
# p5

rm(df, p1, p2, p3, p4, y1_real, y2_real, y3_real, y4_real, Years)


```

***


Part Two: THE DYNAMICS OF THE CAPITAL/INCOME RATIO

- The Metamorphoses of Capital

- FIGURE 3.2

- Page 143

- Context 



